---
title: "Answer to Question 10, DSCI 521, Lab 4"
subtitle: "with xaringan on R Studio"
author: "Arjun Radhakrishnan"
date: "October 1, 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

This slide contains a code chunk which calculates the largest number of a list in R.

```{r}
temps <- list(20.2, 22.3, 19.7, 25.0, 16.3)
max <- temps[[1]]
i <- 1
for (temp in temps) {
    if (max < temp){
        max = temp
    }
    i <- i + 1
}

print(paste0(max, " is largest number in the list"))

```

---

This slide contains a code chunk which calculates the smallest number of a list in R.

```{r}
temps <- list(20.2, 22.3, 19.7, 25.0, 16.3)
min <- temps[[1]]
i <- 1
for (temp in temps) {
    if (min > temp){
        min = temp
    }
    i <- i + 1
}

print(paste0(min, " is smallest number in the list"))

```


---

This slide contains a code chunk which calculates the largest number of a list in python.

```{python}

temps = [20.2, 22.3, 19.7, 25.0, 16.3]
max = temps[0]
i = 0
for temp in temps:
        if max < temp:
            max = temp
        i = i + 1

print(f"{max} is largest number in the list")

```


---
class: center, middle

I'm taking the slide to thank the teaching faculty and the TAs for this awesome course!  

--
THANK YOU!
--

---
